### 2013-09-19 Reports/Report1/data.tex
revise report1

\section{Feedback Data}
After every translation, a pre-selected corrector revises the translation. After reviewing, the corrector assesses the translation and leave a feedback on it. This feedback consists of a comment and number which evaluate the quality of translation from one to five (five is the best). These feedbacks are also categorized in different aspects of translation like content, grammar, style, accuracy and etc. For each translation, the value related to each criterion (price, time, text matching and cooperation) can be fetched from database.

Since the website is working from 2011, there are about 2000 feedback records in database which related to different translators and language pairs.

>>>>

\section{Translation Feedback Data}
After every translation, a pre-selected corrector revises the translation and assesses the translation quality. Then the corrector leaves a feedback on it which consists of a comment and a number from one to five (five is the best) which evaluate the quality of translation. These feedbacks are also categorized in different aspects of translation like content, grammar, style, accuracy and etc. For each translation, criterion values (price, time, text matching and cooperation) offered by translator can be fetched from database.

Since the website is working from 2011, there are about 2000 feedbacks in database. These records contain the assessment of different translators and language pairs in different criterion categories.

### 2013-09-19 Reports/Report1/idea.tex
revise report1

\section{Ideas and Brainstorming}
Using data represented in Appendix A for every translation, a vector can be created that shows the relation between four criteria (time, price, text matching and cooperation) and final feedback. My idea for translators ranking consisted of two elements which both are based on the defined vector. It is formulated as follows where $R_T$ ,$H_T$ and $P_T$ denote ranking value of translator, first element (Harmonic) and second element (Privilege). $\alpha$ is the tuning factor and can be between 0 and 1.

@@

The first element ($H_T$) which can be called Harmonic element shows how similar the vector is to well-ranked results and how far it is from bad-ranked results. The similarity is calculated by cosine measure. In the following formula $O_T$ denotes translator's offer and $F_i$ stands for vector of feedback. For each feedback, the feedback rate is shown in $r_i$. The formula is depicted as follows:

@@

The second element ($P_T$) which can be called Privilege element shows how good the offered criterion in comparison to a standard value is. In order to find the value, we need a Standard Vector ($S$) which can be achieved by calculating the average of all offered values by translators in every criterion. Here is the formulas for calculating $S$ and $G_T$. $O_{T,c}$ stands for offer value by a translator for a specific criterion. The function $f$ is used for normalizing the value. Finally $n$ denotes number of offers by translators

\begin{center}
$S = \sum_{i=0}^{n} \frac{O_{T,c}}{n}$ \\
\end{center}

\begin{center}
$G_T = \sum_{c=0}^{number of criteria} \frac{f(O_{T,c})}{S_c} $ \\
\end{center}

I suggest using $\log _2 \left( x \right)$ as function $f$. The reason for selecting base two is decreasing radically the effect of division when offer is more than two times bigger than standard value. The suggested function is depicted in Figure ~\ref{fig:FUNC} :

>>>>

\section{Ideas and Brainstorming}
Using data represented in Appendix A for every translation, a vector can be created that shows the relation between four criteria (time, price, text matching and cooperation) and final feedbacks. My idea for translators ranking consisted of two elements which both are based on the defined vector. It is formulated as follows where $R_T$ ,$H_T$ and $P_T$ denote ranking value of translator, first element (Harmonic) and second element (Privilege). $\alpha$ is the tuning factor and can be between 0 and 1.

@@

The first element ($H_T$) which can be called Harmonic element shows how similar the vector is to high-ranked results and how far it is from low-ranked results. The similarity is calculated by cosine measure. In the following formula $O_T$ denotes translator's offer and $F_i$ stands for vector of feedback and $r_i$ shows the feedback's rate. The formula is depicted as follows:

@@

The second element ($P_T$) which can be called Privilege element shows how good the offered criteria are in comparison to a standard value. In order to find the value, we need a Standard Vector ($S$) which can be achieved by calculating the average of all offered values by translators in every criterion. Here is the formulas for calculating $S$ and $G_T$. $O_{T,c}$ stands for offered value by a translator for a specific criterion. The function $f$ is used for normalizing the value. Finally $n$ denotes number of translators' offers.

\begin{center}
$S_c = \sum_{i=0}^{n} \frac{O_{T,c}}{n}$ \\
\end{center}

\begin{center}
$G_T = \sum_{c=0}^{number of criteria} f(\frac{O_{T,c}}{S_c}) $ \\
\end{center}

I suggest using $f = \log _2 \left( x \right)$. The reason for selecting base two is decreasing radically the effect of division when offer is more than two times bigger than standard value. The suggested function is depicted in Figure ~\ref{fig:FUNC}.
